---
title: "10-Conclusions"
author: "Benjamin Dupuis"
date: "25/01/2022"
output:
  html_document:
    toc: true
    toc_float: true
    theme: yeti
    highlight: kate
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = F, warning = F)
```

# Study of the effect of anthropogenic activities on little penguins foraging during the breeding season at Phillip island

```{r preambule}
rm(list = ls())
library(tidyverse) ; library(lubridate)
library(lme4) ; library(lmerTest) ; library(dplyr)
library(multcomp) ; library(dplyr) ; library(ggplot2)
library(lattice) ; library(car) ; library(performance)
library(cowplot) ; library(sp) ; library(sf) ; library(ggspatial)
library(gridExtra) ; library(plotly) ; library(viridis)
library(raster) ; library(suncalc) ; library(simmr)
library(SIBER) ; library(ellipse) ; library(sjPlot)
library(nicheROVER);library(SIBER);library(ellipse); library(coda)
library(sp);library(sf);library(ggspatial);library(track2KBA); library(ggpubr); library(rempsyc)
library(MuMIn); library(ggeffects); library(ggpubr); library(cowplot); library(report);library(broom)
```

```{r traffic and spec count}
#Quick plot of data
global_count <- readRDS("Data/global_count.rds")

global_count <- global_count %>% 
  filter(year >= 2010, month(date) >= 9)

global_count$month <- as.factor(month(global_count$date))
global_count$year <- as.factor(global_count$year)
global_count$day <- as.factor(global_count$day)
ggplot(data = global_count, aes(x = as.factor(year), y = spectators)) +
  geom_point() +
  geom_boxplot()

         
marine_df <- readRDS("Data/Marine_traffic/Marine_traffic_2012-2020.rds")
marine_df$timestamp <- dmy_hms(marine_df$timestamp)
marine_df_count <- marine_df %>%
  filter(!is.na(timestamp)) %>% 
  filter(year(timestamp) >= 2014) %>%
  filter(month(timestamp) >= 9) %>%
  mutate(date = date(timestamp)) %>% 
  group_by(date) %>% 
  summarise(n_boat = n()) %>% 
  mutate(year = year(date))

marine_df_count$day <- as.factor(as.character(day(marine_df_count$date)))
marine_df_count$month <- as.factor(as.character(month(marine_df_count$date)))
marine_df_count$year <- as.factor(as.character(year(marine_df_count$date)))

ggplot(data = marine_df_count, aes(x = year, y = n_boat)) +
  geom_point() +
  geom_boxplot()

#Model nspec
n_spec_mod <- lm(spectators ~ month+year,
                   data = global_count,
                 na.action = "na.fail")


mod_select_spec <- dredge(n_spec_mod)
mod_select_spec_print <- nice_table(mod_select_spec[,2:ncol(mod_select_spec)])
flextable::save_as_docx(mod_select_spec_print, path = "R/Figures/final_figures/mod_select_spec.docx")

mod_tab_spec <- as.data.frame(report(n_spec_mod))
mod_tab_spec <- nice_table(mod_tab_spec, short = T)
flextable::save_as_docx(mod_tab_spec, path = "R/Figures/final_figures/summary_spec.docx")

plot_model(n_spec_mod, type = "diag")
plot_model(n_spec_mod, type = "est")
plot_model(n_spec_mod, type = "pred", ci.lvl = 0.95)

summary(glht(n_spec_mod, linfct = multcomp::mcp(month = "Tukey")), test = adjusted("holm"))

#Model nboat
n_boat_mod <- lm(n_boat ~ month+year,
                   data = marine_df_count,
                 na.action = "na.fail")

mod_select_boat <- dredge(n_boat_mod)
mod_select_boat_print <- nice_table(mod_select_boat[,2:ncol(mod_select_boat)])
flextable::save_as_docx(mod_select_boat_print, path = "R/Figures/final_figures/mod_select_boat.docx")

n_boat_mod_final <- lm(n_boat ~ month+year,
                   data = marine_df_count,
                 na.action = "na.fail")

mod_tab_boat <- as.data.frame(report(n_boat_mod_final))
mod_tab_boat <- nice_table(mod_tab_boat, short = T)
flextable::save_as_docx(mod_tab_boat, path = "R/Figures/final_figures/summary_boat.docx")

plot_model(n_boat_mod_final, type = "diag")
plot_model(n_boat_mod_final, type = "est")
plot_model(n_boat_mod_final, type = "pred", ci.lvl = 0.95)

summary(glht(n_boat_mod_final, linfct = multcomp::mcp(year = "Tukey")), test = adjusted("holm"))

#Clean plot
library(ggdist)

spec_plot_mod <- ggplot(global_count, aes(x = as.factor(year), y = spectators)) + 
  geom_violin(fill = "white", width = 1.5) + 
  geom_boxplot(width = .2, outlier.shape = NA, coef = 0, aes(color = covid)) +
  ggforce::geom_sina(method = "counts", alpha = .2) +
  geom_text(x = "2020", y = 1500, label = "***", size = 10) +
  labs(x = "Year",
       y = "Daily number of tourists",
       title = "A.",
       col = "Year with lock-down") +
  theme_pubr() +
  labs_pubr() +
  scale_color_viridis(discrete = T, option = "cividis") +
  theme(legend.title = element_text(size = 20),
        legend.text = element_text(size = 20),
        axis.text = element_text(size = 20),
        text = element_text(size = 20),
        legend.position = "none")
spec_plot_mod
boat_plot_mod <- ggplot(marine_df_count, aes(x = as.factor(year), y = n_boat)) + 
  geom_violin(fill = "white") + 
  geom_boxplot(width = .2, outlier.shape = NA, coef = 0) +
  ggforce::geom_sina(method = "counts", alpha = .2) +
  geom_text(x = "2014", y = 400, label = "***", size = 10) +
  geom_text(x = "2018", y = 600, label = "**", size = 10) +
  labs(x = "Year",
       y = "Daily number of vessels",
       title = "B.") +
  theme_pubr() +
  labs_pubr() +
  theme(legend.title = element_text(size = 20),
        legend.text = element_text(size = 20),
        axis.text = element_text(size = 20),
        text = element_text(size = 20),
        legend.position = "none")

cowplot::plot_grid(spec_plot_mod, boat_plot_mod, ncol = 1)
ggsave("R/Figures/final_figures/fig1.png", units = "mm", width = 80, height = 60, dpi = 600, scale = 3.5)
```


```{r adjust weighbride}
weighbridge <- readRDS("Data/weighbridge.rds") 
daily_count_boat <- marine_df_count 
weighbridge <- weighbridge %>% filter(season >=2014)

weighbridge$breeding_stage <- as.factor(weighbridge$breeding_stage)
weighbridge$breeding_stage <- ordered(weighbridge$breeding_stage, levels = c("Incubation", "Guard", "PG"))

#Calculate arrival and leaving time relatively to sunset/sunrise
weighbridge$hour_out <- as.POSIXct(format(strptime(weighbridge$localtime_out, "%Y-%m-%d %H:%M:%S"), "%H:%M:%S"), format="%H:%M:%S")
weighbridge$hour_in <- as.POSIXct(format(strptime(weighbridge$localtime_in, "%Y-%m-%d %H:%M:%S"), "%H:%M:%S"), format="%H:%M:%S")

colon <-  145.1503  #colony longitude 145.1496 ~ 145.151
colat <-  -38.5103  #colony latitude -38.5106 ~ -38.509

weighbridge$localtime_out <- force_tz(weighbridge$localtime_out, tz = "Australia/Melbourne")
weighbridge$localtime_in <- force_tz(weighbridge$localtime_in, tz = "Australia/Melbourne")

#Prepare the tibble to calculate relative times
my_out <- tibble(date = date(weighbridge$localtime_out), lat = colat, lon = colon, time_out = weighbridge$localtime_out)
my_out$adjust_day <- ifelse(hour(my_out$time_out) > 14, T, F) #Some bird leave early in the night (11pm. We need to tweak the date to have the right sunrise)
my_out$date[which(my_out$adjust_day == TRUE)] <- my_out$date[which(my_out$adjust_day == TRUE)] +1
weighbridge$sunrise <- getSunlightTimes(data = my_out[,1:3], keep = "nauticalDawn", tz = "Australia/Melbourne")[,4]
weighbridge$diff_time_out <- weighbridge$localtime_out - weighbridge$sunrise

#Prepare the tibble to calculate relative times
my_in <- tibble(date = date(weighbridge$localtime_in), lat = colat, lon = colon, time_in = weighbridge$localtime_in)
my_in$adjust_day <- ifelse(hour(my_in$time_in) < 14, T, F) 
my_in$date[which(my_in$adjust_day == TRUE)] <- my_in$date[which(my_in$adjust_day == TRUE)] - 1
weighbridge$sunset <- getSunlightTimes(data = my_in[,1:3], keep = "nauticalDusk", tz = "Australia/Melbourne")[,4]
weighbridge$diff_time_in <- weighbridge$localtime_in - weighbridge$sunset

#Use numeric values in minutes
weighbridge$diff_time_out <- as.numeric(weighbridge$diff_time_out, units = "mins")
weighbridge$diff_time_in <- as.numeric(weighbridge$diff_time_in, units = "mins")

weighbridge$local_date_out <- date(weighbridge$sunrise)-1
weighbridge$local_date_in <- date(weighbridge$sunset)
keep_colnames <- c(colnames(weighbridge), "n_spec", "n_spec_return", "n_boat", "n_boat_return")
weighbridge <- weighbridge %>%
  left_join(daily_count_boat, by = join_by(local_date_in == date)) %>%
  rename(n_boat_return = n_boat) %>% 
  left_join(daily_count_boat, by = join_by(local_date_out == date)) %>% 
  left_join(global_count, by = join_by(local_date_in == date)) %>% 
  rename(n_spec_return = spectators) %>% 
  left_join(global_count, by = join_by(local_date_out == date)) %>% 
  rename(n_spec = spectators) %>% 
  dplyr::select(all_of(keep_colnames))
  
```

```{r plot attendance, echo=FALSE}
arrive_plot <- ggplot(weighbridge, aes(x = as.factor(season), y = diff_time_in)) +
  geom_boxplot() +
  stat_summary(color = "red") +
  theme_bw() +
  geom_hline(yintercept = mean(weighbridge$diff_time_in), linetype = "dashed") +
  facet_grid(~breeding_stage) +
  labs(y = "Arrival out relative to nautical dusk (min)",
       x = "Penguin season") +
  theme(axis.text.x = element_text(angle = -30))

plot(arrive_plot)

leave_plot <- ggplot(weighbridge, aes(x = as.factor(season), y = diff_time_out)) +
  geom_boxplot() +
  stat_summary(color = "red") +
  theme_bw() +
  geom_hline(yintercept = mean(weighbridge$diff_time_out), linetype = "dashed") +
  facet_grid(~breeding_stage) +
  labs(y = "Departure time out relative to nautical dawn (min)",
       x = "Penguin season") +
  theme(axis.text.x = element_text(angle = -30))

plot(leave_plot)


plot_link_leave <- ggplot(weighbridge, aes(x = n_spec, y = diff_time_out, col = as.factor(season))) +
  geom_point(alpha = 0.5) +
  facet_grid(~breeding_stage) +
  theme_bw() +
  labs(y = "Departure time in relative to nautical dawn (min)",
       x = "Average number of spectators in the last 7 days")

plot_link_leave

weighbridge$std_date <- weighbridge$sunrise
year(weighbridge$std_date) <- 2020
weighbridge$std_date <- as_date(weighbridge$std_date)

departure_trend <- ggplot(weighbridge, aes(x = std_date, y = diff_time_out)) +
  geom_point() +
  facet_wrap(~season)

departure_trend

hist(weighbridge$diff_time_out)
```


```{r model attendance}
source("R/toolbox.R")
weighbridge$season <- as.factor(weighbridge$season)
weighbridge$breeding_stage <- as.factor(as.character(weighbridge$breeding_stage))
weighbridge$stage_season <- interaction(weighbridge$season, weighbridge$breeding_stage)

#Departure model#####
weighbridge_departure <- weighbridge %>%
  filter(!is.na(n_spec),
         !is.na(breeding_stage),
         !is.na(season),
         !is.na(diff_time_out),
         !is.na(n_boat))%>% 
  mutate(n_spec = (n_spec - mean(n_spec)) / sd(n_spec),
         n_boat = (n_boat - mean(n_boat)) / sd(n_boat))

grp_dep <- weighbridge_departure %>% group_by(season, breeding_stage) %>% summarise(mean_dep = mean(diff_time_out),
                                                                                    mean_spec = mean(n_spec),
                                                                                    mean_boat = mean(n_boat))
#Model selection
mod_dep <- lm(mean_dep ~ mean_boat + mean_spec + breeding_stage + season,
                   data = grp_dep,
              na.action = "na.fail")

mod_select_dep <- dredge(mod_dep)
mod_select_dep_print <- nice_table(mod_select_dep[,2:ncol(mod_select_dep)])
flextable::save_as_docx(mod_select_dep_print, path = "R/Figures/final_figures/mod_select_dep.docx")


#Final model - only brd_stage
mod_dep_final <- lm(mean_dep ~ breeding_stage,
                    data = grp_dep,
                    na.action = "na.fail")

mod_tab_dep <- as.data.frame(report(mod_dep_final))
mod_tab_dep <- nice_table(mod_tab_dep, short = T)
flextable::save_as_docx(mod_tab_dep, path = "R/Figures/final_figures/summary_dep.docx")
acf(resid(mod_dep_final))

plot(mod_dep_final) #diagnostic plot okay
MuMIn::r.squaredGLMM(mod_dep_final, use.hat = TRUE)

#Only significance difference in the departure time between breeding stages
summary(glht(mod_dep_final, linfct = multcomp::mcp(breeding_stage = "Tukey")), test = adjusted("holm"))

my_pred_dep <- as_tibble(ggpredict(mod_dep_final, terms = "breeding_stage"))

est_dep_plot <- ggplot() +
  geom_jitter(data = grp_dep, aes(x = breeding_stage, y = mean_dep, col = breeding_stage), size = 5, width = 0.15) +
  geom_errorbar(data = my_pred_dep, aes(x = x, ymin = conf.low, ymax = conf.high, col = x), width = 0) +
  geom_point(data = my_pred_dep, aes(x = x, y = predicted, col = x) , shape = 21, size = 7, fill = "white") +
  labs(x = "Breeding stage", y = "Departure time relative to nautical dawn (min)", col = "Breeding stages", title = "A.") +
  scale_x_discrete(labels = c("Guard" = "Guard",
                              "Incubation" = "Incubation",
                              "PG" = "Post-guard"),
                   limits = c("Incubation", "Guard", "PG")) +
  scale_color_viridis(discrete = T,
                      labels = c("Guard" = "Guard",
                                 "Incubation" = "Incubation",
                                 "PG" = "Post-guard"),
                      limits = c("Incubation", "Guard", "PG")) +
  coord_flip() +
  theme_pubr() +
  labs_pubr() +
  theme(legend.title = element_text(size = 30),
        legend.text = element_text(size = 30),
        axis.text = element_text(size = 30),
        text = element_text(size = 30),
        legend.position = "none")
  
est_dep_plot

#Arrival model####
weighbridge_arrival <- weighbridge %>%
  filter(!is.na(n_spec_return),
         !is.na(breeding_stage),
         !is.na(season),
         !is.na(diff_time_in),
         !is.na(n_boat_return)) %>% 
  mutate(n_spec_return = (n_spec_return - mean(n_spec_return)) / sd(n_spec_return),
         n_boat_return = (n_boat_return - mean(n_boat_return)) / sd(n_boat_return))

grp_arr <- weighbridge_arrival %>% group_by(season, breeding_stage) %>% summarise(mean_arr = mean(diff_time_in),
                                                                                    mean_spec = mean(n_spec_return),
                                                                                    mean_boat = mean(n_boat_return))

#Model selection
mod_arr <- lm(mean_arr ~ mean_boat + mean_spec + breeding_stage + season,
                   data = grp_arr,
              na.action = "na.fail")

mod_select_arr <- dredge(mod_arr)
mod_select_arr_print <- nice_table(mod_select_arr[,2:ncol(mod_select_arr)])
flextable::save_as_docx(mod_select_arr_print, path = "R/Figures/final_figures/mod_select_arr.docx")

#Final model - only brd_stage
mod_arr_final <- lm(mean_arr ~ 1,
                    data = grp_arr,
                    na.action = "na.fail")


mod_tab_arr <- as.data.frame(report(mod_arr_final))
mod_tab_arr <- nice_table(mod_tab_arr, short = T)
flextable::save_as_docx(mod_tab_arr, path = "R/Figures/final_figures/summary_arr.docx")
acf(resid(mod_arr_final))
plot(mod_arr_final) #diagnostic plot okay
MuMIn::r.squaredGLMM(mod_arr_final, use.hat = TRUE)

#no significant differences
summary(glht(mod_arr_final, linfct = multcomp::mcp(breeding_stage = "Tukey")), test = adjusted("holm"))

#Plot

grp_arr$dummy <- "dummy"

est_arr_plot <- ggplot() +
  geom_point(data = grp_arr, aes(x = mean_arr, y = mean_spec, col = breeding_stage),size = 5) +
  labs(x = "Arrival time relative to nautical dusk (min)", y = "Standardized number of tourists", title = "B.") +
  scale_color_viridis(discrete = T,
                      labels = c("Guard" = "Guard",
                                 "Incubation" = "Incubation",
                                 "PG" = "Post-guard"),
                      limits = c("Incubation", "Guard", "PG")) +
  theme_pubr() +
  labs_pubr() +
  theme(legend.title = element_text(size = 30),
        legend.text = element_text(size = 30),
        axis.text = element_text(size = 30),
        text = element_text(size = 30),
        legend.position = "none")

est_arr_plot
```

### 2.3 -- Mass variation

#### 2.3.1 -- Over foraging trip (foraging efficiency)

Here, we look at the difference between the mass of the penguin when it leaves the colony to forage and when it comes back at night. This could be therefore a indicator of the foraging efficiency.

Mass gain is normally distributed and there do not seems to be any effect of the amount of spectators.

```{r mass over day - explore}
hist(weighbridge$MassGain)
spec_mass_day <- ggplot(weighbridge, aes(x = n_spec, y = MassGain)) + 
  geom_point()
plot(spec_mass_day)
spec_mass_day_return <- ggplot(weighbridge, aes(x = n_spec_return, y = MassGain)) + 
  geom_point()
plot(spec_mass_day_return)
```

We'll try to fit a LMM.

```{r r mass over day - model}
source("R/toolbox.R")
weighbridge_mass_day <- weighbridge %>% 
  filter(!is.na(n_spec),
         !is.na(n_boat),
         !is.na(breeding_stage),
         !is.na(season),
         !is.na(MassGain))%>% 
  mutate(n_spec = (n_spec - mean(n_spec)) / sd(n_spec),
         n_boat = (n_boat - mean(n_boat)) / sd(n_boat),
         mass_day = MassGain/FT_days)


grp_mass_day <- weighbridge_mass_day %>% group_by(season, breeding_stage) %>% summarise(mean_mass = mean(mass_day),
                                                                                    mean_spec = mean(n_spec),
                                                                                    mean_boat = mean(n_boat))

#Model selection
mod_mass_day <- lm(mean_mass ~ mean_boat + mean_spec + breeding_stage + season,
                   data = grp_mass_day,
              na.action = "na.fail")

mod_select_mass_day <- dredge(mod_mass_day)
mod_select_mass_day_print <- nice_table(mod_select_mass_day[,2:ncol(mod_select_mass_day)])
flextable::save_as_docx(mod_select_mass_day_print, path = "R/Figures/final_figures/mod_select_mass_day.docx")

#Final model - brd satge and boat
mod_mass_day_final <- lm(mean_mass ~ breeding_stage + mean_boat,
                    data = grp_mass_day,
                    na.action = "na.fail")

mod_tab_mass_day <- as.data.frame(report(mod_mass_day_final))
mod_tab_mass_day <- nice_table(mod_tab_mass_day, short = T)
flextable::save_as_docx(mod_tab_mass_day, path = "R/Figures/final_figures/summary_mass_day.docx")
acf(resid(mod_mass_day_final))
plot(mod_mass_day_final) #diagnostic plot okay
MuMIn::r.squaredGLMM(mod_mass_day_final, use.hat = TRUE)

Anova(mod_mass_day_final, type = 2) 
summary(glht(mod_mass_day_final, linfct = multcomp::mcp(breeding_stage = "Tukey")), test = adjusted("holm"))

#Plot
my_pred_mass_day <- as_tibble(ggpredict(mod_mass_day_final, terms = c("mean_boat", "breeding_stage")))

est_mass_day_plot <- ggplot() +
  geom_ribbon(data = my_pred_mass_day, aes(x = x, ymin = conf.low, ymax = conf.high, col = group),linetype = 2, alpha = 0) +
  geom_line(data = my_pred_mass_day, aes(x = x, y = predicted, col = group), size = 1) +
  geom_point(data = grp_mass_day, aes(x = mean_boat, y = mean_mass, col = breeding_stage), size = 5) +
  labs(x = "Standardized number of vessels", y = "Mass gain per day at sea (g)", col = "Breeding stages", title = "C.") +
  scale_color_viridis(discrete = T,
                      labels = c("Guard" = "Guard",
                                 "Incubation" = "Incubation",
                                 "PG" = "Post-guard"),
                      limits = c("Incubation", "Guard", "PG")) +
  theme_pubr() +
  labs_pubr() +
  theme(legend.title = element_text(size = 30),
        legend.text = element_text(size = 30),
        axis.text = element_text(size = 30),
        text = element_text(size = 30),
        legend.position = "none")

est_mass_day_plot
```

#### 2.3.2 -- Overnight (offspring investment)

Same but overnight to look at the chick investment. We still need to had the 2020 season here.

```{r load and arrange data}
overnight <- readRDS("Data/feed_overnight.rds") 

overnight <- overnight %>% filter(season >=2014)

overnight$breeding_stage <- as.factor(overnight$breeding_stage)
overnight$breeding_stage <- ordered(overnight$breeding_stage, levels = c("Incubation", "Guard", "PG"))

#Because we are interested in the investment overnight to the chick, we only keep observations where pengu stayed less than on days at the colony
overnight$time_at_col <- difftime(overnight$datetime_in, overnight$datetime_out, units = "days")
overnight <- overnight %>% filter(time_at_col <= 1, !is.na(Mass.feed))

overnight$local_date_out <- date(overnight$datetime_out)
keep_colnames <- c(colnames(overnight), "n_spec", "n_boat")
overnight <- overnight %>%
  left_join(daily_count_boat, by = join_by(local_date_out == date)) %>%
  left_join(global_count, by = join_by(local_date_out == date)) %>% 
  rename(n_spec = spectators) %>% 
  dplyr::select(all_of(keep_colnames))
```

```{r mass over night - explore}
hist(overnight$Mass.feed)
plot(overnight$Mass.feed, overnight$n_spec)
plot(overnight$Mass.feed, overnight$n_boat)
```

```{r model overnight}
source("R/toolbox.R")
overnight$season <- as.factor(overnight$season)
overnight$breeding_stage <- as.factor(as.character(overnight$breeding_stage))
overnight$stage_season <- interaction(overnight$season, overnight$breeding_stage)

weighbridge_mass_night <- overnight %>%
  filter(!is.na(n_spec),
         !is.na(n_boat),
         !is.na(breeding_stage),
         !is.na(season),
         !is.na(Mass.feed)) %>% 
           mutate(n_spec = (n_spec - mean(n_spec)) / sd(n_spec),
                  n_boat = (n_boat - mean(n_boat)) / sd(n_boat))

grp_mass_night <- weighbridge_mass_night %>% group_by(season, breeding_stage) %>% summarise(mean_mass = mean(Mass.feed),
                                                                                    mean_spec = mean(n_spec),
                                                                                    mean_boat = mean(n_boat))

#Model selection
mod_mass_night <- lm(mean_mass ~ mean_boat + mean_spec + season + breeding_stage,
                   data = grp_mass_night,
              na.action = "na.fail")

mod_select_mass_night <- dredge(mod_mass_night)
mod_select_mass_night_print <- nice_table(mod_select_mass_night[,2:ncol(mod_select_mass_night)])
flextable::save_as_docx(mod_select_mass_night_print, path = "R/Figures/final_figures/mod_select_mass_night.docx")

#Final model - boat
mod_mass_night_final <- lm(mean_mass ~ mean_boat,
                    data = grp_mass_night,
                    na.action = "na.fail")
mod_tab_mass_night <- as.data.frame(report(mod_mass_night_final))
mod_tab_mass_night <- nice_table(mod_tab_mass_night, short = T)
flextable::save_as_docx(mod_tab_mass_night, path = "R/Figures/final_figures/summary_mass_night.docx")
acf(resid(mod_mass_night_final))
plot(mod_mass_night_final) #diagnostic plot okay
MuMIn::r.squaredGLMM(mod_mass_night_final, use.hat = TRUE)

Anova(mod_mass_night_final, type = 2) 

#Plot
my_pred_mass_night <- as_tibble(ggpredict(mod_mass_night_final, terms = c("mean_boat")))

est_mass_night_plot <- ggplot() +
  geom_ribbon(data = my_pred_mass_night, aes(x = x, ymin = conf.low, ymax = conf.high),linetype = 2, alpha = 0, col = "black") +
  geom_line(data = my_pred_mass_night, aes(x = x, y = predicted), size = 1) +
  geom_point(data = grp_mass_night, aes(x = mean_boat, y = mean_mass, col = breeding_stage), size = 5) +
  labs(x = "Standardized number of vessels", y = "Meal size given to chicks (g)", col = "Breeding stages", title = "D.") +
  scale_color_manual(values = c("#21908CFF", "#FDE725FF"),
                      labels = c("Guard" = "Guard",
                                 "PG" = "Post-guard"),
                      limits = c("Guard", "PG")) +
  theme_pubr() +
  labs_pubr() +
  theme(legend.title = element_text(size = 30),
        legend.text = element_text(size = 30),
        axis.text = element_text(size = 30),
        text = element_text(size = 30),
        legend.position = "none")

est_mass_night_plot

```

```{r weighbridge panel}
plot_weighbridge <- cowplot::plot_grid(est_dep_plot, est_arr_plot,est_mass_day_plot, est_mass_night_plot, ncol = 2, nrow = 2, align = "V")

dummy_legend <- ggplot() +
  geom_ribbon(data = my_pred_mass_day, aes(x = x, ymin = conf.low, ymax = conf.high, col = group),linetype = 2, alpha = 0) +
  geom_line(data = my_pred_mass_day, aes(x = x, y = predicted, col = group), size = 1) +
  geom_point(data = grp_mass_day, aes(x = mean_boat, y = mean_mass, col = breeding_stage), size = 5) +
  labs(col = "Breeding stages") +
  scale_color_viridis(discrete = T,
                      labels = c("Guard" = "Guard",
                                 "Incubation" = "Incubation",
                                 "PG" = "Post-guard"),
                      limits = c("Incubation", "Guard", "PG")) +
  theme_pubr() +
  labs_pubr() +
  theme(legend.title = element_text(size = 30),
        legend.text = element_text(size = 30),
        axis.text = element_text(size = 30),
        text = element_text(size = 30))

figure_weighbridge <- cowplot::plot_grid(cowplot::get_legend(dummy_legend), plot_weighbridge, ncol = 1, rel_heights = c(0.1,1))
figure_weighbridge

ggsave(plot =  figure_weighbridge,  filename = "R/Figures/final_figures/fig3.pdf", dpi = 600, width = 180, height = 110, units = "mm", scale = 3.5)
```

### 2.4 -- Diet

We use the package nicheRover here (SIBER can also be use, results are similar). We do not have any clear pattern when looking at the area or the overlap between season-stage. The only thing we see is a gradual temporal change in the niche (seasons close to each other are more overlapping).

```{r diet analysis}
 
# isotope <- read.csv("Data/lp_isotope.csv", sep = ";")
# # Format dataset
# names(isotope) <- tolower(names(isotope))
# isotope <- isotope %>% filter(year >= 2010, b.stage != "Pre-breeding")
# flextable::save_as_docx(nice_table(isotope %>%
#                                      group_by(year, b.stage,sex) %>% 
#                                      summarise(n = n()) %>%
#                                      pivot_wider(names_from = year, values_from = n)), path = "R/Figures/final_figures/sample_isotopes.docx")
# 
# for (my_stage in unique(isotope$b.stage)) {
#   my_iso <- isotope %>% filter(b.stage == my_stage)
#   my_iso$year <- as.factor(my_iso$year)
#   
#   aggregate(my_iso[4:5], my_iso[1], mean) # isotope means calculated for each season
#   
#   # generate parameter draws from the "default" posteriors of each season
#   nsamples <- 1e3
#   system.time({
#     lp.par <- tapply(1:nrow(my_iso), my_iso$year,
#                      function(ii) niw.post(nsamples = nsamples, X = my_iso[ii,4:5]))
#   })
#   
#   # various parameter plots
#   clrs <- viridis(length(levels(my_iso$year))) # colors for each species
#   
#   # mu1 (del13C), mu2 (del15N), and Sigma12
#   par(mar = c(4, 4, .5, .1)+.1, mfrow = c(1,3))
#   niche.par.plot(lp.par, col = clrs, plot.index = 1)
#   niche.par.plot(lp.par, col = clrs, plot.index = 2)
#   niche.par.plot(lp.par, col = clrs, plot.index = 1:2)
#   legend("topleft", legend = names(lp.par), fill = clrs)
#   dev.off()
#   # # all mu (del13C, del15N)
#   # niche.par.plot(lp.par, col = clrs, plot.mu = TRUE, plot.Sigma = FALSE)
#   # legend("topleft", legend = names(lp.par), fill = clrs)
#   # 
#   # # all mu and Sigma
#   # par(mar = c(4.2, 4.2, 2, 1)+.1)
#   # niche.par.plot(lp.par, col = clrs, plot.mu = TRUE, plot.Sigma = TRUE)
#   # legend("topright", legend = names(lp.par), fill = clrs)
#   
#   # 2-d projections of 10 niche regions
#   nsamples <- 10
#   lp.par <- tapply(1:nrow(my_iso), my_iso$year,
#                    function(ii) niw.post(nsamples = nsamples, X = my_iso[ii,4:5]))
#   
#   # format data for plotting function
#   lp.data <- tapply(1:nrow(my_iso), my_iso$year, function(ii) X = my_iso[ii,4:5])
#   
#   niche.plot(niche.par = lp.par, niche.data = lp.data, pfrac = .05,
#              iso.names = expression(delta^{13}*C, delta^{15}*N),
#              col = clrs)
#   mtext("Isotope ratio (‰)", side=4)
#   title(main = my_stage, xlab = "Isotope ratio (‰)")
#   
#   # Overlap is the probability that an individual from season A will be found in the niche of season B.
#   # niche overlap plots for 95% niche region sizes
#   nsamples <- 1000
#   lp.par <- tapply(1:nrow(my_iso), my_iso$year,
#                    function(ii) niw.post(nsamples = nsamples, X = my_iso[ii,4:5]))
#   
#   # Overlap calculation.  use nsamples = nprob = 10000 (1e4) for higher accuracy.
#   # the variable over.stat can be supplied directly to the overlap.plot function
#   over.stat <- overlap(lp.par, nreps = nsamples, nprob = 1e3, alpha = c(.95, 0.99))
#   
#   #The mean overlap metrics calculated across iteratations for both niche 
#   #region sizes (alpha = .95 and alpha = .99) can be calculated and displayed in an array.
#   over.mean <- apply(over.stat, c(1:2,4), mean)*100
#   round(over.mean, 2)
#   
#   over.cred <- apply(over.stat*100, c(1:2, 4), quantile, prob = c(.025, .975), na.rm = TRUE)
#   round(over.cred[,,,1]) # display alpha = .95 niche region
#   
#   # Overlap plot.Before you run this, make sure that you have chosen your 
#   #alpha level.
#   over.stat <- overlap(lp.par, nreps = nsamples, nprob = 1e3, alpha = .95)
#   overlap.plot(over.stat, col = clrs, mean.cred.col = "black", equal.axis = TRUE,
#                xlab = paste0("Overlap Probability (%) - ", my_stage, " - Niche Region Size: 95% "))
# 
#   
#   # Then we can calculate niche size estimates
#   # posterior distribution of (mu, Sigma) for each species
#   nsamples <- 1000
#   lp.par <- tapply(1:nrow(my_iso), my_iso$year,
#                    function(ii) niw.post(nsamples = nsamples, X = my_iso[ii,4:5]))
#   
#   # posterior distribution of niche size by species
#   lp.size <- sapply(lp.par, function(spec) {
#     apply(spec$Sigma, 3, niche.size, alpha = .95)
#   })
#   
#   # point estimate and standard error
#   rbind(est = colMeans(lp.size),
#         se = apply(lp.size, 2, sd))
#   
#   # boxplots
#   boxplot(lp.size, col = clrs, pch = 16, cex = .5, ylab = "Niche Size", xlab = "Seasons", main = my_stage)
# }
```